Phylodynamic inference of contact network parameters through approximate Bayesian computation

### 2016-05-21 doc/thesis/discussion.tex
Most of Alex's changes done

Our implementation of \gls{SMC} uses a simple multinomial scheme to sample
particles from the population according to their weights. Several other
sampling strategies have been developed~\autocite{douc2005comparison}, and it
is possible that the use of a more sophisticated technique might increase the
algorithm's accuracy. Finally, the \gls{ABC}-\gls{SMC} algorithm is
computationally intensive, taking about a day when run on 20 cores in parallel
with the settings described in the methods section. Implementing parallization
using MPI, rather than POSIX threads as we have done here, would allow the
program to be run over a larger number of cores on multiple CPUs in parallel.

\subsection{Analysis of \acrlong{BA} model}

@@

\subsection{Application to HIV data}

>>>>

Our implementation of \gls{SMC} uses a simple multinomial scheme to sample
particles from the population according to their weights. Several other
sampling strategies have been developed~\autocite{douc2005comparison}, and it
is possible that the use of a more sophisticated technique might increase the
algorithm's accuracy. Finally, the \gls{ABC}-\gls{SMC} algorithm is
computationally intensive, taking about a day when run on 20 cores in parallel
with the settings described in the methods section. Implementing
parallelization using MPI, rather than POSIX threads as we have done here,
would allow the program to be run over a larger number of cores on multiple
CPUs in parallel.

\subsection{Analysis of \acrlong{BA} model with synthetic data}

@@

\subsection{Application to real world HIV data}
